title: "Project"
author: "Saurav"
date: "3/23/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Reading the data from The CSV files¶

```{r load}
library(dplyr)

# and visualization
library(tidyverse)
library(tidyr)

  
# package to compute
# cross - validation methods
#install.packages("caret")
library(caret)
library(caTools)
library("aod")
library(pROC)






twitterBots <- read.csv("/Users/saurav/git/data/bots_data.csv", comment.char="#")
twitterNonBots <- read.csv("/Users/saurav/git/data/nonbots_data.csv", comment.char="#")
user <- read.csv("/Users/saurav/git/data/training_data_2_csv_UTF.csv", comment.char="#")
test <- read.csv("/Users/saurav/git/data/test_data_4_students.csv", comment.char="#")


```

## Cleaning Training Data and converting it to boolean & numeric values


```{r cleaing}
library(stringr)
df=user


df$bot[str_detect(df$bot,'bot')] <- FALSE
df$bot[is.na(df$bot)] <- FALSE

df$statuses_count[df$statuses_count=='NONE'] <- 0
df$statuses_count[df$statuses_count==''] <- 0
df$statuses_count[is.na(df$statuses_count)] <-0
df$statuses_count <- as.integer(df$statuses_count)

df$followers_count[is.na(df$followers_count)] <-0

df$friends_count <- as.integer(df$friends_count)
df$friends_count[is.na(df$friends_count)] <- 0

df$verified[df$verified==''] <- FALSE
df$verified[df$verified=='TRUE'] <- TRUE
df$verified[df$verified=='FALSE'] <- FALSE
df$verified[df$verified=='False'] <- FALSE
df$verified[df$verified=='True'] <- TRUE



df$favourites_count[df$favourites_count =='None'] <- 0

df$favourites_count <-as.integer(df$favourites_count)
df$favourites_count[is.na(df$favourites_count)] <- 0


df$default_profile[df$default_profile =='None'] <- FALSE
df$default_profile[df$default_profile ==''] <- FALSE
df$default_profile[df$default_profile =='FALSE'] <- FALSE
df$default_profile[df$default_profile =='False'] <- FALSE
df$default_profile[df$default_profile =='TRUE'] <- TRUE
df$default_profile[df$default_profile =='True'] <- TRUE
df$default_profile[is.na(df$default_profile)] <- FALSE

df$default_profile_image[df$default_profile_image =='None'] <- FALSE
df$default_profile_image[df$default_profile_image ==''] <- FALSE
df$default_profile_image[is.na(df$default_profile_image)] <- FALSE
df$default_profile_image[df$default_profile_image =='True'] <- TRUE
df$default_profile_image[df$default_profile_image =='False'] <- FALSE

df$name[is.na(df$name)] <- ''
df$name[str_detect(df$name,regex('bot',ignore_case = T))] <- FALSE
df$name[df$name==""] <- FALSE
df$name[df$name!="FALSE"] <- TRUE


df$screen_name[is.na(df$screen_name)] <- ''
df$screen_name[str_detect(df$screen_name,regex('bot',ignore_case = T))] <- FALSE
df$screen_name[df$screen_name==""] <- FALSE
df$screen_name[df$screen_name!="FALSE"] <- TRUE

df$description[is.na(df$description)] <- ''
df$description[str_detect(df$description,regex('bot',ignore_case = T))] <- FALSE
df$description[df$description==""] <- FALSE
df$description[df$description!="FALSE"] <- TRUE


library(lubridate)
df$created_at[is.na(df$created_at)] <- '2021-03-29 02:52:00'
df$created_at[df$created_at ==''] <- '2021-03-29 02:52:00'
df$created_at <-  gsub("\\+00:00", "", df$created_at)
df$created_at=parse_date_time(df$created_at, orders = "ymd_HMS")
```
##Calculating the status per day from the day account was created

```{r check status}

df$today <- Sys.Date()
df$created_at<-strptime(df$created_at, format = "%Y-%m-%d")
df$daysTillNow <- as.numeric(difftime(df$today, df$created_at, units = "days"))
df$statusPerDay <- as.integer(df$statuses_count)/df$daysTillNow

df$statusPerDay <-round(df$statusPerDay)
 df<-drop_na(df)




df <- within(df, favourites_count_q <- as.integer(cut(favourites_count, quantile(favourites_count,probs = seq(.2, 1, by = .2)), include.lowest=TRUE)))
df <- within(df, friends_count_q <- as.integer(cut(friends_count, quantile(friends_count,probs = seq(.1, 1, by = .1)), include.lowest=TRUE)))

df <- within(df, statusPerDay_q <- as.integer(cut(statusPerDay, quantile(statusPerDay,probs = seq(.25, 1, by = .25)), include.lowest=TRUE)))

df <- within(df, followers_count_q <- as.integer(cut(followers_count, quantile(followers_count,probs = seq(.1, 1, by = .1)), include.lowest=TRUE)))

df <- within(df, statuses_count_q <- as.integer(cut(statuses_count, quantile(statuses_count,probs = seq(.1, 1, by = .1)), include.lowest=TRUE)))

df$favourites_count_q[is.na(df$favourites_count_q)] <- 0
df$friends_count_q[is.na(df$friends_count_q)] <- 0

df$statusPerDay_q[is.na(df$statusPerDay_q)] <- 0

df$followers_count_q[is.na(df$followers_count_q)] <- 0

df$statuses_count_q[is.na(df$statuses_count_q)] <- 0



```



  


##Splitting the data

```{r splitting the data }
#install.packages('caTools')

#We Split the sample data in the ratio of 70:30

split = sample.split(df$bot,
                      SplitRatio = .70)

#70% of sample data includes the training set and rest 30% is test set
training_set = subset(df, split == TRUE)
test_set = subset(df, split == FALSE)
```




##Fitting the training data and predicting test data contained in training data and the test data from using logistic regression
```{r fitting model}

summary(df)


training_set$bot <-factor(training_set$bot)
logit_twitter <- glm(bot ~  favourites_count_q+ friends_count_q +statusPerDay_q +followers_count_q +   verified  + name + screen_name + description,
                     data = training_set, family = binomial(link = "logit"))

summary(logit_twitter)

                             




```




```{r glm}
confint(logit_twitter)

wald.test(b = coef(logit_twitter), Sigma = vcov(logit_twitter), Terms = 4:6)


exp(coef(logit_twitter))

exp(cbind(OR = coef(logit_twitter), confint(logit_twitter)))


```
##predicting 
```{r predict}
 
# package to perform data manipulation
logit_twitter.pred <-predict(logit_twitter, test_set, type="response")

logit_twitter.pred <- ifelse(logit_twitter.pred > .50, 1, 0)

data.frame( R2 = R2(logit_twitter.pred, test_set$bot),
            RMSE = RMSE(logit_twitter.pred, test_set$bot),
            MAE = MAE(logit_twitter.pred, test_set$bot))

attach(test_set)
table(logit_twitter.pred,bot)

mean(logit_twitter.pred == bot)

#install.packages("proc")
library(pROC)

twitterBots <- roc(test_set$bot, logit_twitter.pred)
auc(twitterBots)

```